Turbulence in compact to giant HII regions

### 2022-06-28 Corr.tex
Javier changes 2022-06-28

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
    log $r_0$ &       log $S$ &   0.95 $\pm$ 0.33 &  -1.68 $\pm$ 0.71 &   0.86 &  0.003 \\
 log $\sigma$ &      log L(H) &   0.26 $\pm$ 0.11 &  -9.19 $\pm$ 4.33 &   0.86 &  0.003 \\
 log $\sigma$ &       log $S$ &   0.24 $\pm$ 0.17 &   0.24 $\pm$ 0.38 &   0.64 &   0.06 \\
 log $\sigma$ &   log $r_{0}$ &   0.18 $\pm$ 0.17 &   0.69 $\pm$ 0.12 &   0.51 &  0.164 \\
      log $m$ &      log Dist &  -0.02 $\pm$ 0.04 &   0.04 $\pm$ 0.08 &   -0.4 &   0.29 \\
      log $m$ &  log $\sigma$ &  -0.18 $\pm$ 1.03 &   0.14 $\pm$ 0.74 &  -0.37 &  0.327 \\
      log $m$ &   log $r_{0}$ &  -0.02 $\pm$ 0.07 &   0.01 $\pm$ 0.05 &  -0.28 &  0.469 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

>>>>

\begin{table*}
\begin{center}
\caption{Linear regressions values in the form Y = aX + b between our turbulent parameters obtained using the chi-square statistic and properties of each region (Table \ref{tab:regions-properties}). The fifth column, $r$, is the Pearson correlation coefficient and the last column is the $p$-value. This results were obtained using the procedure in \citet{2007ApJ...665.1489K}.}
\begin{tabular}{cccccc}
\hline
            $Y$ &                   $X$ &                 $a$ &                 $b$ &       $r$ &      $p$ \\
\hline
      log $r_0$ &         log $S$ &   0.95 $\pm$ 0.33 &  -1.68 $\pm$ 0.71 &   0.86 &  0.003 \\
   log \(\sigma\pos\) &        log L(H\(_\alpha\)) &    0.28 $\pm$ 0.1 &  -9.87 $\pm$ 3.78 &   0.86 &  0.003 \\
 \(\sigma\pos\) &  $\sigma_{\text{los}}$ &   1.03 $\pm$ 0.46 &     7.7 $\pm$ 2.9 &   0.79 &   0.01 \\
   log \(\sigma\pos\) &         log $S$ &   0.25 $\pm$ 0.17 &    0.2 $\pm$ 0.38 &   0.64 &   0.06 \\
        log $m$ &        log Dist &  -0.02 $\pm$ 0.04 &   0.04 $\pm$ 0.08 &   -0.4 &   0.29 \\
       \(\sigma\pos\) &         $r_{0}$ &    0.4 $\pm$ 0.65 &   4.68 $\pm$ 3.08 &   0.37 &  0.329 \\
            $m$ &        \(\sigma\pos\) &  -0.02 $\pm$ 0.03 &   1.12 $\pm$ 0.21 &  -0.37 &  0.331 \\
            $m$ &         $r_{0}$ &   0.02 $\pm$ 0.03 &   0.95 $\pm$ 0.16 &  -0.09 &  0.824 \\
\bottomrule
\end{tabular}\label{tab:RestStats}
\end{center}
\end{table*}

### 2022-06-28 strucfunc_paper.tex
Javier changes 2022-06-28

\newcommand\ha{\ensuremath{\text{H}\alpha}}
\newcommand\Wav[1]{\ensuremath{\lambda #1}}
% Chemical formulae
\newcommand*\chem[1]{\ensuremath{\mathrm{#1}}}
\newcommand\csound{\ensuremath{c_{\text{s}}}}

@@

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. Sizes taken from Table 2 of \citet{1984ApJ...287..116K}. Reference from the other properties are mentioned in the text.}
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d& \text{Size,}\ S & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &   6 \pm 1      \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   13.6 \pm 0.8    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   22.4 \pm 2.7    \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &   31.7     \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &   10.1     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   13.4     \\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   12.3     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   18.3 \pm 5.7     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   16.2 \pm 7.7     \\
\bottomrule
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

Table~\ref{tab:regions-properties} summarises the properties of the regions in our sample
with data taken from the literature. Further details on each individual source is given in Appendix~\ref{sec:notes-individual-hii}.

@@

%methods for our analysis
In section \ref{sec:results} we show that each velocity field of our sample can be characterized by parameters that are particular for each \hii{} region.
We used these parameters to develop scaling relations between them and the physical properties of each region.
To accomplish this we implement a hierarchical Bayesian model for fitting a straight line using the \texttt{linmix} Python library based on \cite{2007ApJ...665.1489K}.
We use the physical properties in Table \ref{tab:regions-properties} as the independent variable \(X\) and the turbulent parameters in Table \ref{tab:Res} as the dependent variable \(Y\).
In the following analysis we left out the EON to avoid redundancy in the fitting.
For the physical properties we consider an uncertainty of the \num{10}\% of the value and for the turbulent parameters we use the 2-\(\sigma\) intervals. 
In the case of non-gaussian distribution we choose the highest value for the uncertainty.
The main results are shown in Table \ref{tab:RestStats} in ascending order for the \(p\)-value.
In the Figures \ref{fig:sigvsl} and \ref{fig:rvsR} we show the correlations with a significance level \(p < \num{0.05}\) which corresponds to the first two rows in Table \ref{tab:RestStats}.
In the Figures the black solid line shows the input regression line and the red thin lines show some samples from the posterior distribution.

%Luminosity vs centroid velocity dispersion
The Figure \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
Our results give us a relation of \(\log \sigma\pos = (0.26 \pm 0.11) \log \text{L}(\text{H}_{\alpha})-(9.3 \pm 4.3)\).
It is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable.
In our case if we choose the upper uncertainty and take the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{2.6}\). 
Using the same procedure in \textit{linmix} and changing the variables order we obtained \(\log \text{L}(\text{H}_{\alpha}) = (3.9\pm 2.6) \log \sigma\pos -(35.55 \pm 2)\) which is within the uncertainty of the previously proposed \(\text{L}_{\text{H}} \propto \sigma^{4}\) relations.
The references for the \(\text{L}(\text{H}_{\alpha})\) value are given in Appendix~\ref{sec:notes-individual-hii}.

@@

%Size vs centroid velocity dispersion
Other important relation commonly used in the study of the interstellar medium is the diameter (or size) versus velocity dispersion.
Table \ref{tab:RestStats} shows this result for our sample in row 3. 
This relation presents a significance level \(p > \num{0.05}\) but there are a couple of things worth mentioning.
Historically this relation is important following the work of \citet{1981MNRAS.194..809L} where he presents it in the context of molecular cloud complexes of many clouds, individual clouds, and clumps, so that size scales are studied over \(\num{0.1} < L < \SI{100}{pc}\) obtaining \(\sigma = 1.10 L ^{0.38}\). 
This relation is interpreted in terms of turbulence, particularly the Kolmogorov model which predicts a index of \num{0.33} so that larger regions presents more turbulence, and smaller regions less turbulence.
It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium (see first paragraph of this section).
On the other hand, we obtain \(\log \sigma\pos = (0.24 \pm 0.17) \log S - (0.24 \pm 0.38)\) which despite the large uncertainty is comparable with previous investigations.

%power-law index
Finally, as for the power-law index \(m\) we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property, being the least reliable parameter for determining or concluding something about the nature of the physical processes inside the regions.

@@

\subsection{Relationship between plane-of-sky and mean line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}

@@

In the Figure~\ref{fig:los-vs-pos} we show the mean line-of-sight velocity dispersion versus the plane-of-sky velocity dispersion. 
\citet{arthur2016turbulence} presents the same diagram for different emission lines of the Orion core nebula showing that the value \(\sigma_{\text{los}}\) is roughly twice as the \(\sigma\pos\) (figure 14 on their work), while the \citet{2011MNRAS.413..705L} diagram, for a sample of small-to-intermediate size \hii{} regions in M33, approach unity (figure 4 on their work). 
The Figure~\ref{fig:los-vs-pos} shows that for our sample of \hii{} regions the parameters follows a \(\sigma_{\text{los}}\) = \(n \sigma_{\text{pos}}\) relation with \(3 > n > 1\).

The case of the reduction in the \(\sigma\pos\) can be interpreted by the effect of \textit{project smearing} \citep{1984ApJ...277..556S}.
If we consider the case of homogeneous turbulent velocity, the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
This procedure implies depths of the order 10 to 50 times the correlation length.
In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency of this interpretation for the Orion core nebula, since evidence has shown that the emitting layer thickness is of the order of \num{0.01} - \SI{0.3}{pc}.
For the most distant regions of our sample, the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (see section~\ref{sec:power-index}) only NGC 595, which power-law index is \num{1.38}, would comply to this fully three-dimensional structure.
On the other hand, \citet{arthur2016turbulence} proposed another interpretation in terms of large-scale, order motions and emissivity fluctuations.
They consider an expanding shell where the mean velocity fluctuations on the plane of the sky are because the relative brightness of the redshifted and blueshifted hemispherers.
In this case, the rms fractional variation in the emissivity on the scale diameter is found to be in the order of \(\sigma\pos / \sigma_{\text{los}}\).

@@

The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}}\citep{1984ApJ...287..116K}.
It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}. 
The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}. 
The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.

@@

The 30 Doradus (Tarantula Nebula) nebula is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
The central ionized region spans for \SI{40}{pc} and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
This nebula is commonly used as a comparison for extragalactic star-forming regions.

@@

\subsection{Hubble X and Hubble V in NGC 6822}
\label{sec:6822-hubble}
%
The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter). %(1'' = 2.4 pc)
%HV has a characteristic length of 100 pc and HX has a characteristic length of 140 pc \citep{1999PASP..111.1382O}.
Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
Two recognized OB associations are identified within these HII regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.

%HV has a luminosity at its core of in L$_{H_\alpha}$ = 1 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ 
%HX has a luminosity at its core of in L$_{H_\alpha}$ = 2.4 $\times$ 10$^{49}$ H$\alpha$ photons s$^{-1}$ \citep{1999PASP..111.1382O}.

@@

NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a big loop, big shells and different size filaments.
It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
For the northern cluster they find eight luminous stars and no evolved massive stars.
More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
This suggest that two episodes of star formation, at least, have taken place in the GEHR.

@@

NGC 595 is the second brightest giant HII region in the M33 galaxy and has an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
It has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
\citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 
Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
They derived and age of 4.5\(\pm\)1.0 Myr consistent with \citet{1993AJ....105.1400D}.
\citet{2010MNRAS.402.1635R} used Integral Field Spectroscopy (IFS) to present a resolved study of the physical properties of the ionized gas and the ionized structure.
They also confirm the presence of previous cataloged WR stars and detect new candidates, and propose classical emission-line ratios as metallicity calibrators.
\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations.
They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.

>>>>

\newcommand\ha{\ensuremath{\text{H}\alpha}}
\newcommand\Wav[1]{\ensuremath{\lambda #1}}
% Chemical formulae
\newcommand*\chem[1]{\ensuremath{\mathrm{#1}}}
\newcommand\csound{\ensuremath{c_{\text{s}}}}
\newcommand\FNa{\textsuperscript{a}}

@@

\begin{table}
\begin{center}\caption{Summary of properties of our \hii{} region sample. Sizes taken from Table 2 of \citet{1984ApJ...287..116K}. Reference from the other properties are mentioned in the text.}
\begin{tabular}{cCCCC}\toprule
\hii{}    &  \text{Distance,}\ d& \text{Size,}\ S & \log L(\ha) &  \langle \sigma\los \rangle \\
  Region    &  [\si{kpc}]          &  [\si{pc}]    &  [\si{erg.s^{-1}}]            &    [\si{km.s^{-1}}]  \\ 
\midrule
Orion     & 0.436 \pm 0.02  & 5 \pm 0.5    &    37.18       &   9.9 \pm 1.2\FNa        \\
Lagoon    & 1.25 \pm 0.12   & 25 \pm 2.5      &    37.47    &   11.7 \pm 1.6    \\
Carina    & 2.35 \pm 0.05   & 200 \pm 20      &    38.54    &   18.6 \pm 3.3\FNa      \\
30 Dor    & 50.0 \pm 0.2    & 370 \pm 37    &    39.46    &   22 \pm 2.2    \\
NGC 346   & 62 \pm 1        & 220 \pm 22      &    38.77    &   10.1 \pm 1.0     \\
Hubble X  & 490 \pm 40      & 160 \pm 16      &    38.21    &   10.5 \pm 0.02\\
Hubble V  & 490 \pm 40      & 130 \pm 13      &    38.3     &   10.3 \pm 0.03     \\
NGC 595   & 820 \pm 30      & 400 \pm 40      &    38.95    &   16.8 \pm 0.1     \\
NGC 604   & 820 \pm 30      & 400 \pm 40      &    39.42    &   17.8 \pm 0.30     \\
\bottomrule
\multicolumn{5}{l}{\FNa{}Value obtained from our observations.}
\end{tabular}\label{tab:regions-properties}
\end{center}
\end{table}

Table~\ref{tab:regions-properties} summarizes the properties of the regions in our sample
with data taken from the literature. Further details on each individual source and references are given in Appendix~\ref{sec:notes-individual-hii}.

@@

%methods for our analysis
In section \ref{sec:results} we show that each velocity field of our sample can be characterized by parameters that are particular for each \hii{} region.
We used these parameters to develop scaling relations between them and the physical properties of each region.
To accomplish this we implement a hierarchical Bayesian model for fitting a straight line using the \texttt{linmix} Python library based on \cite{2007ApJ...665.1489K}.
We use the physical properties in Table \ref{tab:regions-properties} as the independent variable \(X\) and the turbulent parameters in Table \ref{tab:Res} as the dependent variable \(Y\).
In the following analysis we left out the EON to avoid redundancy in the fitting process.
For the physical properties we consider an uncertainty of \num{10}\% of the values for the size and the mean non-thermal linewidths for 30 Doradus and NGC 346.
For the turbulent parameters we use the relative error considering the 2-\(\sigma\) intervals. 
In the case of non-gaussian distribution we choose the highest value for the uncertainty.
The main results are shown in Table \ref{tab:RestStats} in ascending order for the \(p\)-value.
In the Figures \ref{fig:sigvsl}, \ref{fig:rvsR} and \ref{fig:los-vs-pos} we show the plots for the correlations with a significance level \(p < \num{0.05}\) which corresponds to the first three rows in Table \ref{tab:RestStats}.
In the Figures the black solid line shows the input regression line with its equation and the red thin lines show some samples from the posterior distribution.

%Luminosity vs centroid velocity dispersion
The Figure \ref{fig:sigvsl} shows the log \(\sigma\pos\)-log \(\text{L}(\text{H}_{\alpha})\) plane.
The references for the \(\text{L}(\text{H}_{\alpha})\) value are given in Appendix~\ref{sec:notes-individual-hii}.
Since this relation is the most common it can be use for comparison with the investigations mentioned at the beginning of this section.
Our results give us a relation of \(\log \sigma\pos = (0.27 \pm 0.10) \log \text{L}(\text{H}_{\alpha})-(9.9 \pm 4.0)\).
It is customary in the literature to present \(\text{L} (\text{H}_{\alpha})\) as the dependent variable.
In our case if taking the inverse of slope we have \(\text{L}_{\text{H}_{\alpha}} \propto \sigma^{3.6}\). 
Using the same procedure in \textit{linmix} and changing the variables order we obtained \(\log \text{L}(\text{H}_{\alpha}) = (2.8\pm 1.0) \log \sigma\pos -(36 \pm 4)\).
Both values are close to the \(\text{L}_{\text{H}} \propto \sigma^{4}\) relations.
The fact that this relation

@@

%Size vs centroid velocity dispersion
Other important relation commonly used in the study of the interstellar medium is the diameter (or size) versus velocity dispersion.
Table \ref{tab:RestStats} shows this result for our sample in the forth row. 
This relation presents a significance level \(p > \num{0.05}\) but there are a couple of things worth mentioning.
Historically this relation is important following the work of \citet{1981MNRAS.194..809L} where he presents it in the context of molecular cloud complexes of many clouds, individual clouds, and clumps, so that size scales are studied over \(\num{0.1} < L < \SI{100}{pc}\) obtaining \(\sigma = 1.10 L ^{0.38}\). 
This relation is interpreted in terms of turbulence, particularly the Kolmogorov model which predicts a index of \num{0.33} so that larger regions presents more turbulence, and smaller regions less turbulence.
It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium (see first paragraph of this section).
On the other hand, we obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log S - (0.2 \pm 0.38)\) which despite the large uncertainty is comparable with previous investigations within the error.

%power-law index
As for the power-law index \(m\) we can see from table \ref{tab:RestStats} that this parameter does not correlate with any other parameter or physical property, being the least reliable for determining or concluding something about the nature of the physical processes inside the regions.
On the other hand, the lack of correlation and the presence of the power-law index may be interpreted as a universal property of the velocity fluctuations independent of the observed object, which is the main consideration in the turbulence theory.

@@

\subsubsection{Relationship between plane-of-sky and mean line-of-sight velocity dispersion}\label{sec:sigmapos-vs-sigmalos}

@@

In the Figure~\ref{fig:los-vs-pos} we show the mean line-of-sight velocity dispersion versus the plane-of-sky velocity dispersion. 
\citet{arthur2016turbulence} presents the same diagram for different emission lines of the Orion core nebula showing that the value \(\sigma_{\text{los}}\) (after considering the dust scattering) is roughly twice as the \(\sigma\pos\) (figure 14 on their work), while the \citet{2011MNRAS.413..705L} diagram, for a sample of small-to-intermediate size \hii{} regions in M33, approach unity (figure 4 on their work). 
The Figure~\ref{fig:los-vs-pos} shows that for our sample of \hii{} regions the fit we obtained follows the result of \citet{2011MNRAS.413..705L}.
The relationship we found is \( \langle \sigma\los \rangle = (1.03 \pm 0.46) \sigma\pos - (7.7 \pm 2.9)\).

The case of the reduction in the \(\sigma\pos\) can be interpreted by the effect of \textit{project smearing} \citep{1984ApJ...277..556S}.
If we consider the case of homogeneous turbulent velocity, the projection from three to two dimensions over the line-of-sight depth \(H\), reduces the plane-of-sky amplitude for the condition \(r_{0} < H\).
With a value of \(\sigma\pos / \sigma_{\text{los}}\) = 0.5 we obtain \(r_{0} / H \sim\) 0.02 - 0.1.
This procedure implies depths of the order 10 to 50 times the correlation length.
In the lower limit \citet{arthur2016turbulence} mentioned the inconsistency of this interpretation for the Orion core nebula, since evidence has shown that the emitting layer thickness is of the order of \num{0.01} - \SI{0.3}{pc}.
For the most distant regions of our sample, the previous analysis would give depths of the order of magnitude of the observational box, but considering the analysis using the power-law index (see section~\ref{sec:power-index}) only NGC 595, which power-law index is \num{1.38}, would comply to this fully three-dimensional structure.
On the other hand, \citet{arthur2016turbulence} proposed another interpretation in terms of large-scale order motions, and emissivity fluctuations.
They consider an expanding shell where the mean velocity fluctuations on the plane of the sky are because the relative brightness of the redshifted and blueshifted hemispherers.
In this case, the rms fractional variation in the emissivity on the scale diameter is found to be in the order of \(\sigma\pos / \sigma_{\text{los}}\).

@@

The Lagoon Nebula (M8, NGC6523) is located at a distance of 1 250 pc \citetext{\SI{1}{\arcsecond} = \SI{0.006}{pc} ; \citealp{2005A&A...430..941P}}.
It has a luminosity in \ha{} of \SI{e37.47}{erg.s^{-1}} \citep{1984ApJ...287..116K}.
The mean non-thermal linewidth in \ha{} is \SI{11.7 \pm 1.6}{km.s^{-1}} \citep{1973ApJ...183..851B}.
It contains the young stellar cluster NGC6530 and the region is illuminated by different massive stars of spectral types O and B, the hottest being 9 Sgr, type O4V \citep{Damiani:2017b}.
Optically, the brightest part of the nebula is called 'Hourglass nebula' which surrounds and obscures the O7 star Herschel 36 \citep{1986AJ.....91..870W}. 
The velocity field shows several expanding shells, related to the stellar population, and the massive protostar M8East-IR \citep{1984ApJ...278..170S} indicating that recent star formation. 
A blueshifted, neutral layer is also in very good agreement with predictions of champagne-flow models of blister HII regions \citep{Damiani:2017b}. 
The properties of the nebula are reviewed by \citet{2008hsf2.book..533T}.

@@

The 30 Doradus (Tarantula Nebula) nebula is located at a distance of \SI{49.9}{kpc} \citetext{\SI{1}{\arcsecond} = \SI{0.24}{pc} ; \citealp{2013Natur.495...76P}}.
It is a luminous star-forming region in the LMC (Large Magellanic Cloud) and is the most luminous complex in the Local Group \citep{1984ApJ...287..116K}.
The central ionized region spans for \SI{40}{pc} and host the massive, dense star cluster R136 %\citep{1991IAUS..148..145W}. %Note: check the bibliographic format
The ionizing output \(Q_0\) of R136 is \SI{e51.4}{photons.s^{-1}} \citep{2020MNRAS.499.1918B}.
The mean non-thermal linewidth in \ha{} is \SI{22}{km.s^{-1}} \citep{2013A&A...555A..60T}.
It host the active star forming region NGC 2070 \citep{2013AJ....145...98W} where the star-formation rate has recently peaked \citep{2015ApJ...811...76C}. 
NGC 2070 host a population of OB and WR stars \citep{2011A&A...530A.108E}.
This nebula is commonly used as a comparison for extragalactic star-forming regions.

@@

\subsection{Hubble X and Hubble V in NGC 6822}
\label{sec:6822-hubble}
%
The irregular dwarf galaxy, NGC 6822, is located at a distance of 500 kpc \citetext{\SI{1}{\arcsecond} = \SI{2.42}{pc} ; \citealp{2012A&A...540A.135S}} and the brightest HII regions are Hubble X and Hubble V (HX and HV hereafter). %(1'' = 2.4 pc)
Luminosity \ha{} for HV is \SI{e38.3}{erg.s^{-1}} and for HX is \SI{e38.21}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
The mean non-thermal linewidth in \ha{} is \SI{10.5 \pm 0.02}{km.s^{-1}} for HX and \SI{10.3 \pm 0.03}{km.s^{-1}} \citep{1986A&A...160..374H}.
Two recognized OB associations are identified within these HII regions \citep{1991ApJ...379..621H,1992AJ....104.1374W}.
HV is located near 'Hodge OB 8' and HX is located near 'Hodge OB13'  \citep{1999PASP..111.1382O}.
\citet{1993PASJ...45..693T} realize a study on the kinematics of HX and HV.

@@

NGC 604 is the second brightest \hii{} region in the Local Group after 30~Dor in the Large Magellanic Cloud and is forty times larger ($\sim $ 400 pc) and 6,000 times brighter than Orion in our Milky Way galaxy.
It is the brightest giant \hii{} region in the M33 galaxy and is visually dominated by a big loop, big shells and different size filaments.
It has a luminosity in \ha{} of \SI{e39.42}{erg.s^{-1}} \citep{2002MNRAS.329..481B}.
The mean non-thermal linewidth in \ha{} is \SI{17.8 \pm 0.3}{km.s^{-1}} \citep{1986A&A...160..374H}.
Using photometry from the HST \citet{1996ApJ...456..174H} identified that the stars are separated into a primary cluster within NGC 604, and a secondary to the north of the region.
In the primary there are \(\sim\)200 OB stars, candidate to red supergiants (RSGs) and the presence of WR stars.
For the northern cluster they find eight luminous stars and no evolved massive stars.
More Recently, \citet{2011MNRAS.411..235E} studied 10 WR stars and propose at least 4 RSGs candidates.
\citet{2012AJ....143...43F} focused on the massive young stellar objects (MYSOs).
The average ages for the stars, was determined to be from  \num{3} to \SI{5}{Myr} \citep{1996ApJ...456..174H} and with the RSGs as an older population have an age of 12.4\(\pm\)2.1 Myr \citep{2011MNRAS.411..235E}.
This suggest that two episodes of star formation, at least, have taken place in the GEHR.

@@

NGC 595 is the second brightest giant HII region in the M33 galaxy and has an \ha{} shell morphology that is related to the stellar winds of the several massive stars located in its interior.
It has a luminosity in \ha{} of \SI{e38.95}{erg.s^{-1}}\citep{2002MNRAS.329..481B}.
The mean non-thermal linewidth in \ha{} is \SI{16.8 \pm 0.1}{km.s^{-1}} \citep{lagrois2009multi}.
\citet{1993AJ....105.1400D} use optical photometry to propose 11 WR stars. 
Using HST/WFPC-2 images \citet{1996AJ....111.1128M} found approximately 250 stars of the OB type, 13 Supergiants and 10 WR, confirming previous candidates.
They derived and age of 4.5\(\pm\)1.0 Myr consistent with \citet{1993AJ....105.1400D}.
\citet{2010MNRAS.402.1635R} used Integral Field Spectroscopy (IFS) to present a resolved study of the physical properties of the ionized gas and the ionized structure.
They also confirm the presence of previous cataloged WR stars and detect new candidates, and propose classical emission-line ratios as metallicity calibrators.
\citet{lagrois2011} present a kinematic study of the regions using optical emission lines and and radio 21 cm line observations.
They proposed Champagne flows at the periphery of the molecular cloud leading to accelerated ionized material.
